Our Galactocentric Reference Frame Is Probably Wrong, and Not by a Little

### 2018-12-04 paper/ms.tex
Update paper

\newcommand{\mi}{\texttt{m12i}}
\newcommand{\mf}{\texttt{m12f}}
\newcommand{\mm}{\texttt{m12m}}
\newcommand{\gdr}{{\em Gaia} DR2}

@@

\section{Introduction} \label{sec:intro}
Our understanding of the Milky Way is currently undergoing a revolution in the era of \gdr. Recent major discoveries include the remnants of a major merger \citep{2018Natur.563...85H}, a phase-space spiral (\Gus{cites}) indicating local substructure infall (\Gus{cites}), a gap indicative of a dark matter subtructure in GD1 \citep{2018arXiv181103631B}, and \Gus{others}.

\section{Reference Frame Gone Wrong} \label{sec:ref_frame}
We begin by quantifying how

@@

Even though we change the center, we do not recalculate the center velocity.
This is largely irrelevant, as the recalculated center velocity differs from
the fiducial center velocity by $<0.1\,\kms$.

>>>>

\newcommand{\mi}{\texttt{m12i}}
\newcommand{\mf}{\texttt{m12f}}
\newcommand{\mm}{\texttt{m12m}}

@@

\section{Introduction} \label{sec:intro}
Our understanding of the Milky Way is currently undergoing a revolution in the
era of {\em Gaia} DR2. Recent major discoveries include the remnants of a
major merger \citep{2018Natur.563...85H}, a phase-space spiral (\Gus{cites})
indicating local substructure infall (\Gus{cites}), a gap indicative of a dark
matter subtructure in GD1 \citep{2018arXiv181103631B}, and \Gus{others}.

Underlying all of these discoveries is the assumption of a galactocentric
reference frame \citep{2008gady.book.....B}. In angular
coordinates, the center of the galaxy is taken to be the location of
Sgr~A\textsuperscript{*} \citep[e.g.][]{2004ApJ...616..872R}. From stellar
motions near Sgr~A\textsuperscript{*}, the distance to the center is taken to
be $\sim 8.1\text{--}8.3\,\kpc$
\citep{2009ApJ...692.1075G,2018A&A...615L..15G}. The vertical height is found
by identifying where the stellar positions and velocities reach a maximum
(effectively the median height of all disk stars), and is usually taken to be
$\sim 25\,\pc$ \citep{2001ApJ...553..184C}, with more recent measurements from
{\em Gaia} DR2 placing it at $\sim 20\,\pc$ \citep{2019MNRAS.482.1417B}.

These measurements of the galactocentric reference frame rely on the
assumption of an axisymmetric Milky Way. Under this assumption, these
estimates would provide the correct parameters for the galactocentric
reference frame up to measurement error. However, the Milky Way is not
axisymmetric in detail. Spiral arms, bar(s), and infalling satellite galaxies
such as Sagittarius and the Large Magellanic Cloud all induce
non-axisymmetries.

Since the Milky Way is not truly axisymmetric, it is not clear the best way to
define the galactocentric reference frame. In this work, we consider one
possible physically motivated approach to defining the galactocentric
reference frame, and show that it can differ from conventional methods of
frame measurements.

In a slowly-evolving axisymmetric potential, the actions of stars' orbits are
conserved quantities \citep{2008gady.book.....B,2014RvMP...86....1S}. In other
words, if we could measure the actions of a star in such a potential, we would
measure the same actions over the course of the orbit. The non-axisymmetries
of a more realistic potential induce time evolution in the {\em measured}
actions --- the true orbital invariants (if they exist) are invariant by
definition. Through simple tests, we will see that even in a truly
axisymmetric potential, if the wrong reference frame is assumed then there
will be additional time evolution in the measured actions.

To provide one such realization of a realistic Galactic potential, we turn to
cosmological zoom-ins of Milky Way-mass galaxies from the Feedback in
Realistic Environments (FIRE)
collaboration\footnote{\url{https://fire.northwestern.edu}} (the Latte suite
of simulations).

\section{Reference Frame Gone Wrong} \label{sec:ref_frame}
We show and quantify the time evolution of measured actions that comes about
from inaccuracies in the galactocentric reference frame.

\subsection{Cartoon} \label{ssec:cartoon}
We begin with a cartoon illustrating what we mean in Figure~\ref{fig:cartoon}.
The solid gray line indicates a hypothetical ``true'' orbit. The y-axis
corresponds to the vertical height of the orbit and the x-axis to either time
or orbital phase. The dashed gray line is an incorrect midplane which an
observer uses to compute orbits.

Now suppose this observer makes a measurement of the true orbit at the orange
point or the red point. Then the orange and red lines correspond to the orbits
that the observer would compute for each point. In action space, this would
correspond to a different value of $J_z$ for the orange and red points. In
this way, assuming the wrong reference frame induces time dependence in the
actions {\em computed by an observer}.

\begin{figure*}
\plotone{cartoon.pdf}
\caption{Caption.}
\label{fig:cartoon}
\end{figure*}

\subsection{Quantification} \label{ssec:quant}
We now turn to classical orbital integration in a commonly assumed Milky Way potential to quantify the time variation of computed actions for different reference frame errors.

@@

Even though we change the center, we do not recalculate the center velocity.
This is largely irrelevant, as the recalculated center velocity differs from
the fiducial center velocity by $<0.1\,\kms$. In recentering the galaxy, the
package \texttt{gizmo\_analysis} will subtract a slightly different value for
the Hubble flow from each particle's velocity to convert to a physical
reference frame. The error this introduces is $\sim 0.02\,\kms$, which we also
ignore.
